---
title: "Lab6"
author: "Yutian Fang"
date: "11/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(broom)
library(equatiomatic)
```

## Example of a rank-based test

We'll make our own samples, using a pseudorandom generator.
```{r}
set.seed(1414)
gp_1 <- sample.int(20, size = 15, replace = TRUE)

set.seed(1424)
gp_2 <- sample.int(30, size = 15, replace = TRUE)
```

```{r}
hist(gp_1)

hist (gp_2)
```

Try a t_test
```{r}
t.test(gp_1, gp_2)
```

meaning of p_value: p value means if these samples were drawn from population with the same mean, the probability of taking two random samples with means*at leaset as different* as the sample means we found by random chance (taking into account spread, n) is 19.82%

Retain (fail to reject) the null hypothesis. >> There is no significance difference in means between group 1 and group 2

warning: people get weirdly upset if you say "accept" the null.

Now let's compare this outcome to a rank-based test

## Mann Whitney U unpaired rank-based test
```{r}
mwU <- wilcox.test(gp_1, gp_2)

mwU
```

If these samples were drawn from populations with the same ranks (medians), the probability of finding two samples with ranks*at least as different* as those in our sample is: 0.28. 

There is no significant differences in ranks (medians) between group 1 and group 2 (statistical summary). 

Median scores for group 1(M = 14) and group2 (M = 12) did not differs significantly (Mann Whittney U test: U(df) = 86, p = 0.28). 



